Playing Atari with Keras and R

### 2018-07-13 article.Rmd

Put in simple terms, Q-learning is an algorithm that allows for the selection of the best possible action to perform given the current state of the environment. It works by assigning each state an estimated value **(Q-value)**. Then, by interacting with the state and receiveing a reward, the estimated value is updated. We can write this Q-value as $\mathbf{Q(s, a)}$ and the updates are given by $\mathbf{Q(s, a) = Q(s, a) + α(R(s) + γmax_{a'}Q(s_0, a_0) − Q(s, a))}$

>>>>

Put in simple terms, Q-learning is an algorithm that allows for the selection of the best possible action to perform given the current state of the environment. It works by assigning each state an estimated value **(Q-value)**. Then, by interacting with the state and receiveing a reward, the estimated value is updated. We can write this Q-value as $\mathbf{Q(s, a)}$ and the updates are given by $\mathbf{Q(s, a) = Q(s, a) + \alpha(R(s) + γmax_{a'}Q(s_0, a_0) − Q(s, a))}$ (more information about the mathematics and the workings of the Q-learning algorithm can be found [here](http://neuro.cs.ut.ee/demystifying-deep-reinforcement-learning/)).

As we have to keep track of the Q-values for every state, storing and updating them in a Q-table, Q-learning can become very ineffective for bigger environments. That's where Deep Q-Learning comes into play, substituting the enormous Q-table for a lighter Neural Network.
